MS_CNuptake.Rmd

### 2022-10-18 MS_CNuptake.Rmd
update

@@

#ORCHIDEE-CNP
nc_flip_lat <- function(nc){

  nc$lat <- rev(nc$lat)

  # nlat <- length(nc$lat)
  # nc$vars[[1]] <- nc$vars[[1]][,nlat:1]

  arr_flip_lat <- function(arr){
    nlat <- dim(arr)[2]
    arr <- arr[,nlat:1]
    return(arr)
  }
  nc$vars <- purrr::map(nc$vars[1], ~arr_flip_lat(.))

  return(nc)
}
ORCHICNP_fNup <- as.data.frame(nc_to_df(read_nc_onefile("~/data/trendy/v8/ORCHIDEE-CNP_S2_fNup_ANN_mean.nc"), varnam = "fNup"))
ORCHICNP_GPP <- as.data.frame(nc_to_df(read_nc_onefile("~/data/trendy/v8/ORCHIDEE-CNP_S2_gpp_ANN_mean.nc"), varnam = "gpp"))
ORCHICNP_NPP <- as.data.frame(nc_to_df(read_nc_onefile("~/data/trendy/v8/ORCHIDEE-CNP_S2_npp_ANN_mean.nc"), varnam = "npp"))

@@

  sp_sites_new <- raster::extract(df1_global, sp_sites, sp = TRUE) %>% as_tibble() %>% 
    right_join(sitemean, by = c("lon", "lat"))
  sitemean_final[,i+2] <- sp_sites_new[,1]
}

>>>>

#produce forest NUE vs. forest BP-leaf/BP
nue_f_output <- npp_f/nuptake_f
lnpp_allocation_f_output <- lnpp_f/anpp_f
data_output <- as.data.frame(cbind(nue_f_output,lnpp_allocation_f_output))
ggplot(data=data_output, aes(x=lnpp_allocation_f_output, y=nue_f_output))+
  geom_point()+
  geom_smooth(method="lm")+xlab("Leaf-BP/ABP")+ylab("NUE")+
  theme(axis.text=element_text(size=10),axis.title=element_text(size=15))
ggsave(paste("./output/figs8.jpg",sep=""),width = 5, height = 5)

@@

#ORCHIDEE-CNP
ORCHICNP_fNup <- as.data.frame(nc_to_df(read_nc_onefile("~/data/trendy/v8/ORCHIDEE-CNP_S2_fNup_ANN_mean.nc"), varnam = "fNup"))
ORCHICNP_GPP <- as.data.frame(nc_to_df(read_nc_onefile("~/data/trendy/v8/ORCHIDEE-CNP_S2_gpp_ANN_mean.nc"), varnam = "gpp"))
ORCHICNP_NPP <- as.data.frame(nc_to_df(read_nc_onefile("~/data/trendy/v8/ORCHIDEE-CNP_S2_npp_ANN_mean.nc"), varnam = "npp"))

@@

  sp_sites_new <- raster::extract(df1_global, sp_sites, sp = TRUE) %>% as_tibble() %>% 
    right_join(sitemean, by = c("lon", "lat"))
  sitemean_final[,i+2] <- sp_sites_new[,1]
}
#for some maps that may not be directly extract from above, using an alternative method (checked that both method should have the same results)
